---
title: "Noise"
author: "Bo Shen"
date: "7/15/2022"
output: html_document
---

## Set the root directory
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/bs3667/Dropbox (NYU Langone Health)/CESS-Bo/AnalysisII')
```

## define directories
```{r}
# data_dir <- '/Users/bs3667/Documents/Projects/Noise/CESS-Bo/TaskProgram/log/txtDat'
data_dir <- '/Users/bs3667/Dropbox (NYU Langone Health)/CESS-Bo/TaskProgram/log/txtDat'
out_dir <- '/Users/bs3667/Dropbox (NYU Langone Health)/CESS-Bo/AnalysisII'
```
# load data
```{r}
filelistbid <- list.files(path = data_dir, pattern = 'BidTask_')
filelistchoice <- list.files(path = data_dir, pattern = 'MainTask_')
grpbid <- c()
grpdcsn <- c()
for (s in 1:length(filelistbid))
{
  indvbid <- read.table(file.path(data_dir,filelistbid[s]), head = TRUE, sep = '\t')
  grpbid <- rbind(grpbid,indvbid)
  indvdcsn <- read.table(file.path(data_dir,filelistchoice[s]), head = TRUE, sep = '\t')
  grpdcsn <- rbind(grpdcsn,indvdcsn)
}
```
## check data
```{r}
subjlist <- unique(grpbid$subID)
Nsubj <- length(subjlist)

# normalize within subjects
bidmax <- aggregate(bid ~ subID, data = grpbid, FUN = max)
grpbid$normbid <- 0
for (subi in 1:Nsubj)
{
  indvmask <- grpbid$subID == subjlist[subi]
  grpbid$normbid[indvmask] <- grpbid$bid[indvmask]/bidmax$bid[bidmax$subID == subjlist[subi]]
}
par(mfrow = c(2,1))
barx <- boxplot(normbid ~ subID, data = grpbid, las = 2)
normbidvar <- aggregate(normbid ~ subID, data = grpbid, FUN = sd)
barplot(normbid ~ subID, las = 2, data = normbidvar, col = 8)
dev.copy(pdf,file.path(out_dir,sprintf("BidQuality.pdf")), height=8, width=12)
dev.off()

blacklist <- c() # pick out the subjects whos bidding on the precise targets (the highest 6 items) are all zero
for (subi in 1:Nsubj)
{
  indvdat <- grpbid[grpbid$subID == subjlist[subi],]
  itemmean <- aggregate(bid ~ item + patch + Group, data = indvdat, FUN = mean)
  itemmean$touch <- itemmean$patch == itemmean$Group
  bidord <- order(itemmean$bid)
  itemmean$ord <- bidord
  itemmean <- itemmean[bidord,]
  items <- 1:36
  plot(items, itemmean$bid, type = 'l', main = subjlist[subi])
  points(items[itemmean$bid > 0], itemmean$bid[itemmean$bid > 0], pch = 20)
  preciseitems <- itemmean$item[itemmean$touch == TRUE]
  loc <- rank(itemmean$ord[itemmean$touch == TRUE]) > 12
  mask <- itemmean$item %in% preciseitems[loc]
  points(items[mask],itemmean$bid[mask], pch = 1, col = 2)
  if (all(itemmean$bid[mask] == 0))
  {
    blacklist <- c(blacklist, subjlist[subi])
  }
}
blacklist <- c(blacklist, '22102708', '22071913', '22110306')
# 22071913 bid all V3 as zero, 22102708 bid all v3 and five targets as zero, 22110306 bid one of the targets as zero
grpbid <- grpbid[!grpbid$subID %in% blacklist,]
str(grpbid)
Ngroup <- aggregate(Group ~ subID, data = grpbid, FUN = unique)
subID <- unique(grpbid$subID)
grpdcsn <- grpdcsn[!grpdcsn$subID %in% blacklist,]
str(grpdcsn)
```
## change the types of some variables
Curious about the types of variables? see <https://rcompanion.org/handbook/C_01.html>
```{r}
grpbid$touched <- factor(as.numeric(grpbid$Group == grpbid$patch), level = c(1,0))
grpbid$Group <- as.factor(grpbid$Group)
grpbid$subID <- as.factor(grpbid$subID)
grpbid$trial <- as.factor(grpbid$trial)
grpbid$item <- as.factor(grpbid$item)
# check again after change
str(grpbid)
```

## Bidding task
# see patterns of multiple bidding on the same items
```{r}
bid1 <- grpbid[grpbid$bid_times == 1,]
bid2 <- grpbid[grpbid$bid_times == 2,]
bid3 <- grpbid[grpbid$bid_times == 3,]
long <- merge(bid1, bid2, by = c('subID','item'))
long <- merge(long, bid3, by = c('subID','item'))
par(mfrow = c(2,2))
plot(long$bid.x, long$bid.y, pch = 20, cex = .3, xlab = 'bid 1', ylab = 'bid 2')
plot(long$bid, long$bid.y, pch = 20, cex = .3, xlab = 'bid 3', ylab = 'bid 2')
plot(long$bid.x, long$bid, pch = 20, cex = .3, xlab = 'bid 1', ylab = 'bid 3')
dev.copy(pdf,file.path(out_dir,'Bid123.pdf'),height=8, width=8)
dev.off()
```

## Calculate the variability of participants' rating, as a function of the bid mean value
```{r}
meanbid <- aggregate(bid ~ item + touched +  subID, FUN = mean, data = grpbid)
sdbid <- aggregate(bid ~ item + touched + subID, FUN = sd, data = grpbid)
```

# visualize individual bidding behavior
```{r}
Indvdir <- file.path(out_dir, 'IndvBid')
if (!file.exists(Indvdir))
{dir.create(Indvdir)}

# individual
for (s in 1:length(subID))
{
  plot(meanbid$bid[meanbid$subID == subID[s] & meanbid$touched == 1],sdbid$bid[sdbid$subID == subID[s] & meanbid$touched == 1], pch = 20, col = 'red', xlab = 'Bid mean', ylab = 'Bid variance', main = subID[s])
  points(meanbid$bid[meanbid$subID == subID[s] & meanbid$touched == 0],sdbid$bid[sdbid$subID == subID[s] & meanbid$touched == 0], pch = 20, col = 'blue')
  legend('topleft',c('Touched (Precise)','Untouched (Vauge)'), text.col = c('red','blue'), pch = 20, cex = .8, col = c('red','blue'), bty = 'n')
  # save the figure
  dev.copy(pdf,file.path(out_dir,'IndvBid',sprintf("BidVariance%s.pdf",subID[s])),height=4, width=4)
  dev.off()
}
```
# Statistics on bidding behavior
```{r, echo=FALSE}
test <- aov(bid ~ touched + Error(subID), data = sdbid)
#summary(test)
require(lmerTest)
Htest <- lmer(bid ~ touched + (1|subID), data = sdbid)
#summary(Htest)
mrgdat <- merge(meanbid, sdbid, by = c('subID','item','touched'))
mrgdat$bidmean <- mrgdat$bid.x
mrgdat$bidvar <- mrgdat$bid.y
Rgtest <- lmer(bidvar ~ bidmean * touched + (1|subID), data = mrgdat)
summary(Rgtest)
```
# visualize bidding behavior as a group
```{r}
redtrnsp <- rgb(255,0,0,50, maxColorValue = 255)
bluetrnsp <- rgb(0,0,255,50, maxColorValue = 255)
# group overlay
for (s in 1:length(subID))
{
  indvdat <- mrgdat[mrgdat$subID == subID[s],]
  patchdat <- indvdat[indvdat$touched == 1,]
  if (s == 1){plot(patchdat$bid.x, patchdat$bid.y, pch = 20, col = 'red', xlab = 'Bid mean', ylab = 'Bid variance', xlim = c(0,80), ylim = c(0,20))}else{points(patchdat$bid.x,patchdat$bid.y, pch = 20, col = redtrnsp)}
  abline(lm(bid.y ~ bid.x, data = patchdat), col = redtrnsp)
  patchdat <- indvdat[indvdat$touched == 0,]
  points(patchdat$bid.x, patchdat$bid.y, pch = 20, col = bluetrnsp)
  abline(lm(bid.y ~ bid.x, data = patchdat), col = bluetrnsp)
}
patchdat <- mrgdat[mrgdat$touched == 1,]
abline(lm(bid.y ~ bid.x, data = patchdat), col = 'red', lwd = 3)
patchdat <- mrgdat[mrgdat$touched == 0,]
abline(lm(bid.y ~ bid.x, data = patchdat), col = 'blue', lwd = 3)

# legend('topleft',c('Interactive','Noninteractive'), text.col = c('red','blue'), pch = 20, cex = .8, col = c('red','blue'), bty = 'n')
# save the figure
dev.copy(pdf,file.path(out_dir,sprintf("SfNPstr_BidVarianceII.pdf")),height=3, width=3)
dev.off()
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Choice task
# data transformation
```{r}
grpdcsn$Group <- as.factor(grpdcsn$Group)
grpdcsn$subID <- as.factor(grpdcsn$subID)
grpdcsn$Vagueness <- as.factor(grpdcsn$Vagueness)
grpdcsn$TimePressure <- as.factor(grpdcsn$TimePressure)
grpdcsn$VD <- grpdcsn$V2 - grpdcsn$V1 # in the design, V2 is always larger than V1
grpdcsn$choice <- grpdcsn$chosenItem - 1 # choose #1 coded as 0 (incorrect); choose #2 coded as 1 (correct); choose #3 coded as 2, discard; NaN choice not made

grpdcsn$normv3 <- grpdcsn$V3/(grpdcsn$V1 + grpdcsn$V2)*2
grpdcsn$V1scld <- grpdcsn$V1
grpdcsn$V2scld <- grpdcsn$V2
grpdcsn$V3scld <- grpdcsn$V3
subjlist <- unique(grpdcsn$subID)
for (s in subjlist)
{
  mask <- grpdcsn$subID == s
  maxval <- max(c(grpdcsn$V1[mask],grpdcsn$V2[mask],grpdcsn$V3[mask]))
  minval <- min(c(grpdcsn$V1[mask],grpdcsn$V2[mask]))
  grpdcsn$V1scld[mask] <- grpdcsn$V1[mask]/minval
  grpdcsn$V2scld[mask] <- grpdcsn$V2[mask]/minval
  grpdcsn$V3scld[mask] <- grpdcsn$V3[mask]/minval
}
grpdcsn$VDscld <- grpdcsn$V2scld - grpdcsn$V1scld
# discard the trials where V1 == V2
grpdcsn <- grpdcsn[grpdcsn$V1 != grpdcsn$V2,]
str(grpdcsn)
```

# Statistical testing, conditional choice accuracy over scaled V3
```{r}
mtest <- lmer(choice ~ VDscld + VDscld:V3scld +  VDscld:V3scld:Vagueness:TimePressure + TimePressure + Vagueness + (1|subID), data = grpdcsn[grpdcsn$choice == 1 | grpdcsn$choice == 0,])
summary(mtest)
```


## regression on the scaled value of ID3
```{r}
Indvdir <- file.path(out_dir, 'IndvChoice')
if (!file.exists(Indvdir))
{dir.create(Indvdir)}

subID <- unique(grpdcsn$subID)
Vagueness <- unique(grpdcsn$Vagueness)
TimePressure <- unique(grpdcsn$TimePressure)
AccID3 <- c()
Rgress <- c()
for (s in 1:length(subID))
{
  par(mfrow = c(2,2))
  indvdat <- grpdcsn[grpdcsn$subID == subID[s],]
  vi <- 0
  for (v in Vagueness) # decision noise
  {
    vi <- vi + 1
    tpi <- 0
    for (tp in TimePressure) # representation noise
    {
      tpi <- tpi + 1
      sectdat <- indvdat[indvdat$TimePressure == tp & indvdat$Vagueness == v & indvdat$chosenItem != 3 & !is.na(indvdat$chosenItem),]
      v3ID <- unique(sectdat$ID3)
      acc <- aggregate(choice ~ ID3, data = sectdat, FUN = mean)
      colnames(acc) <- c('ID3','acc')
      Ntrial <- aggregate(trial ~ ID3, data = sectdat, FUN = length)
      colnames(Ntrial) <- c('ID3','Ntrial')
      bid <- aggregate(V3scld ~ ID3, data = sectdat, FUN = mean)
      onesect <- merge(acc, bid, by = 'ID3')
      onesect <- merge(onesect, Ntrial, by = 'ID3')
      plot(acc ~ V3scld, data = onesect, xlab = 'Mean bid V3', ylab = '% Correct | (1, 2)', pch = 20, cex = (onesect$Ntrial)/10, main = sprintf('%s %s', v, tp))
      test <- lm(acc ~ V3scld, data = onesect, weights = Ntrial)
      if (!is.na(test$coefficients[2])){abline(test)}
      Rgress <- rbind(Rgress, data.frame(subID = subID[s], Vagueness = v, TimePressure = tp, t(test$coefficients)))
      AccID3 <- rbind(AccID3, data.frame(subID = subID[s], Vagueness = v, TimePressure = tp, onesect))
    }
  }
  dev.copy(pdf,file.path(out_dir,'IndvChoice',sprintf("Choice~IDV3scld %s.pdf", subID[s])),height=6, width=6)
  dev.off()
}
par(mfrow = c(2,2))
Rgress$Vagueness <- factor(Rgress$Vagueness, levels = levels(grpdcsn$Vagueness))
Rgress$TimePressure <- factor(Rgress$TimePressure, levels = levels(grpdcsn$TimePressure))
plot(Rgress$V3[Rgress$Vagueness == 'Precise' & Rgress$TimePressure == 'High'], Rgress$V3[Rgress$Vagueness == 'Vague' & Rgress$TimePressure == 'Low'], pch = 20, xlab = 'Precise & High Pressure', ylab = 'Vague & Low Pressure')
lines(c(-1,1),c(0,0), lty = 2)
lines(c(0,0),c(-1,1), lty = 2)
boxplot(V3scld ~ Vagueness + TimePressure, data = Rgress)
myaov <- aov(V3scld ~ Vagueness*TimePressure + Error(subID), data = Rgress)
summary(myaov)
boxplot(X.Intercept. ~ Vagueness + TimePressure, data = Rgress)
myaov <- aov(X.Intercept. ~ Vagueness*TimePressure + Error(subID), data = Rgress)
summary(myaov)
dev.copy(pdf,file.path(out_dir,sprintf("Choice~IDV3scldtomin.pdf")),height=6, width=6)
dev.off()
```

## regression on the value of ID3
```{r}
subID <- unique(grpdcsn$subID)
Vagueness <- unique(grpdcsn$Vagueness)
TimePressure <- unique(grpdcsn$TimePressure)
AccID3 <- c()
Rgress <- c()
for (s in 1:length(subID))
{
  par(mfrow = c(2,2))
  indvdat <- grpdcsn[grpdcsn$subID == subID[s],]
  vi <- 0
  for (v in Vagueness) # decision noise
  {
    vi <- vi + 1
    tpi <- 0
    for (tp in TimePressure) # representation noise
    {
      
      tpi <- tpi + 1
      sectdat <- indvdat[indvdat$TimePressure == tp & indvdat$Vagueness == v & indvdat$chosenItem != 3 & !is.nan(indvdat$chosenItem),]
      
      v3insect <- sectdat$V3
      v3ID <- unique(sectdat$ID3)
      acc <- aggregate(choice ~ ID3, data = sectdat, FUN = mean)
      colnames(acc) <- c('ID3','acc')
      Ntrial <- aggregate(trial ~ ID3, data = sectdat, FUN = length)
      colnames(Ntrial) <- c('ID3','Ntrial')
      bid <- aggregate(V3 ~ ID3, data = sectdat, FUN = mean)
      onesect <- merge(acc, bid, by = 'ID3')
      onesect <- merge(onesect, Ntrial, by = 'ID3')
      plot(acc ~ V3, data = onesect, xlab = 'Mean bid V3', ylab = '% Correct | (1, 2)', pch = 20, cex = (onesect$Ntrial)/10, main = sprintf('%s %s', v, tp))
      test <- lm(acc ~ V3, data = onesect, weights = Ntrial)
      if (!is.na(test$coefficients[2])){abline(test)}
      Rgress <- rbind(Rgress, data.frame(subID = subID[s], Vagueness = v, TimePressure = tp, t(test$coefficients)))
      AccID3 <- rbind(AccID3, data.frame(subID = subID[s], Vagueness = v, TimePressure = tp, onesect))
    }
  }
  dev.copy(pdf,file.path(out_dir,'IndvChoice',sprintf("Choice~IDV3 %s.pdf", subID[s])),height=6, width=6)
  dev.off()
}
par(mfrow = c(2,2))
Rgress$Vagueness <- factor(Rgress$Vagueness, levels = levels(grpdcsn$Vagueness))
Rgress$TimePressure <- factor(Rgress$TimePressure, levels = levels(grpdcsn$TimePressure))
plot(Rgress$V3[Rgress$Vagueness == 'Precise' & Rgress$TimePressure == 'High'], Rgress$V3[Rgress$Vagueness == 'Vague' & Rgress$TimePressure == 'Low'], pch = 20, xlim = c(-.03,.03), ylim = c(-.03,.03), xlab = 'Precise & High Pressure', ylab = 'Vague & Low Pressure')
lines(c(-1,1),c(0,0), lty = 2)
lines(c(0,0),c(-1,1), lty = 2)
boxplot(V3 ~ Vagueness + TimePressure, data = Rgress)
myaov <- aov(V3 ~ Vagueness*TimePressure + Error(subID), data = Rgress)
summary(myaov)
boxplot(X.Intercept. ~ Vagueness + TimePressure, data = Rgress)
myaov <- aov(X.Intercept. ~ Vagueness*TimePressure + Error(subID), data = Rgress)
summary(myaov)
dev.copy(pdf,file.path(out_dir,sprintf("Choice~IDV3.pdf")),height=6, width=6)
dev.off()
```
# Pool subjects, choice accuracy as scaled V3
```{r}
AccID3 <- c()
Rgress <- c()
subID <- unique(grpdcsn$subID)
Vagueness <- unique(grpdcsn$Vagueness)
TimePressure <- unique(grpdcsn$TimePressure)
#par(mfrow = c(2,2))
vi <- 0
for (v in Vagueness) # decision noise
{
  vi <- vi + 1
  tpi <- 0
  for (tp in TimePressure) # representation noise
  {
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    tpi <- tpi + 1
    sectdat <- grpdcsn[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$chosenItem != 3 & !is.nan(grpdcsn$chosenItem),]
    acc <- aggregate(choice ~ V3scld, data = sectdat, FUN = mean)
    colnames(acc) <- c('V3scld','acc')
    Ntrial <- aggregate(trial ~ V3scld, data = sectdat, FUN = length)
    colnames(Ntrial) <- c('V3scld','Ntrial')
    onesect <- merge(acc, Ntrial, by = 'V3scld')
    # onesect <- onesect[onesect$V3scld > 0,]
    if (vi == 1 & tpi == 1){plot(acc ~ V3scld, data = onesect, xlab = 'V3 scaled', ylab = '% Correct | (1, 2)', pch = 20, cex = (onesect$Ntrial)/10, type = 'n', main = sprintf('%s %s', v, tp))}
    test <- lm(acc ~ V3scld, data = onesect, weights = Ntrial)
    if (!is.na(test$coefficients[2])){abline(test, col = mycol)}
    Rgress <- rbind(Rgress, data.frame(Vagueness = v, TimePressure = tp, t(test$coefficients)))
    AccID3 <- rbind(AccID3, data.frame(Vagueness = v, TimePressure = tp, onesect))
  }
}
legend('topleft',c('Precise:Low','Vague:Low','Precise:High','Vauge:High'), text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Choice~IDV3scldtominval_Pool.pdf")),height=4, width=4)
dev.off()
```
# Sliding windows, unweighted
```{r}
vi <- 0
for (v in Vagueness) # decision noise
{
  vi <- vi + 1
  tpi <- 0
  for (tp in TimePressure) # representation noise
  {
    tpi <- tpi + 1
    # if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    # if (v == 'Precise' & tp == 'High'){mycol <- 'magenta'}
    # if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    # if (v == 'Vague' & tp == 'High'){mycol <- 'cyan'}
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    onesect <- AccID3[AccID3$Vagueness == v & AccID3$TimePressure == tp,] #   & AccID3$V3scld > 0.2
    acc <- c()
    Ntrial <- c()
    v3vec <- seq(0,1,.015)
    for (v3 in v3vec)
    {
      mask <- onesect$V3scld > v3 -.15 & onesect$V3scld < v3 + .15
      Ntrial <- rbind(Ntrial, sum(mask)*15)
      acc <- rbind(acc, mean(onesect[mask,]$acc))
    }
    cut <- Ntrial > 80
    if (vi == 1 & tpi == 1){plot(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol, xlim = c(0, 1.1), ylim = c(.60,.75), xlab = 'Sliding window on scaled V3', ylab = '% Correct | (1, 2)')}else{points(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol)}
    lines(v3vec[cut], acc[cut], col = mycol)
    # V1 <- grpdcsn$V1scld[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$choice <= 1 & grpdcsn$V3scld > 0]
    # V2 <- grpdcsn$V2scld[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$choice <= 1 & grpdcsn$V3scld > 0]
    # y <- .78 + ((vi-1)*2 + tpi)/40*rep(1, length(V1))
    # points(V1, y - .005, col = mycol, pch = 20, cex = .3)
    # points(V2, y, col = mycol, pch = 17, cex = .3)
  }
}
legend('bottom',c('Precise:Low','Vague:Low','Precise:High','Vauge:High'), cex = .8, text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Choice~IDV3scldtomin_SldWndwUnwght.pdf")),height=4, width=4)
dev.off()
```
# Sliding windows, weighted
```{r}
Sldwndwdat <- c()
vi <- 0
for (v in Vagueness) # decision noise
{
  vi <- vi + 1
  tpi <- 0
  for (tp in TimePressure) # representation noise
  {
    tpi <- tpi + 1
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    onesect <- AccID3[AccID3$Vagueness == v & AccID3$TimePressure == tp,] #  & AccID3$V3scld > 0.2
    acc <- c()
    Ntrial <- c()
    v3vec <- seq(0,1,.015)
    for (v3 in v3vec)
    {
      mask <- onesect$V3scld > v3 -.15 & onesect$V3scld < v3 + .15
      Ntrial <- rbind(Ntrial, sum(mask)*15)
      acc <- rbind(acc, weighted.mean(onesect[mask,]$acc,onesect[mask,]$Ntrial))
    }
    Sldwndwdat <- rbind(Sldwndwdat, data.frame(v3 = v3vec[cut], acc = acc[cut], Ntrial = Ntrial[cut], TimePressure = tp, Vagueness = v))
    cut <- Ntrial > 200
    if (vi == 1 & tpi == 1){plot(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol, xlim = c(0, 1.1), ylim = c(.6,.73), xlab = 'Sliding window on scaled V3', ylab = '% Correct | (1, 2)')}else{points(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol)}
    lines(v3vec[cut], acc[cut], col = mycol)
    test <- lm(acc[cut] ~ v3vec[cut], weights = Ntrial[cut])
    abline(test, col = mycol)
    # V1 <- grpdcsn$V1scld[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$choice <= 1 & grpdcsn$V3scld > 0]
    # V2 <- grpdcsn$V2scld[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$choice <= 1 & grpdcsn$V3scld > 0]
    # y <- .78 + ((vi-1)*2 + tpi)/40*rep(1, length(V1))
    # points(V1, y - .005, col = mycol, pch = 20, cex = .3)
    # points(V2, y, col = mycol, pch = 17, cex = .3)
  }
}
legend('bottom',c('Precise-Low','Vague-Low','Precise-High','Vauge-High'), cex = .8, text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Choice~IDV3scldtomin_SldWndwWght.pdf")),height=4, width=4)
dev.off()

Sldwndwdat$TimePressure <- factor(Sldwndwdat$TimePressure, levels = c('Low','High'))
Sldwndwdat$Vagueness <- factor(Sldwndwdat$Vagueness, levels = c('Precise','Vague'))

summary(test <- lm(acc ~ v3*Vagueness, weights = Ntrial, data = Sldwndwdat[Sldwndwdat$TimePressure == 'Low',]))
summary(test <- lm(acc ~ v3*Vagueness, weights = Ntrial, data = Sldwndwdat[Sldwndwdat$TimePressure == 'High',]))
summary(test <- lm(acc ~ v3*TimePressure, weights = Ntrial, data = Sldwndwdat[Sldwndwdat$Vagueness == 'Precise',]))
summary(test <- lm(acc ~ v3*TimePressure, weights = Ntrial, data = Sldwndwdat[Sldwndwdat$Vagueness == 'Vague',]))
```

# Sliding windows, weighted, Accuracy normalized within subjects
```{r}
AccID3norm <- AccID3
for (si in unique(AccID3$subID))
{
  indvmask <- AccID3$subID == si
  accsect <- aggregate(acc ~ V3scld, data = AccID3[indvmask,], FUN = mean)
  smlestacc <- accsect$acc[accsect$V3scld == min(accsect$V3scld)]
  AccID3norm$acc[indvmask] <- AccID3$acc[indvmask] - smlestacc
}

Sldwndwdat <- c()
vi <- 0
for (v in Vagueness) # decision noise
{
  vi <- vi + 1
  tpi <- 0
  for (tp in TimePressure) # representation noise
  {
    tpi <- tpi + 1
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    onesect <- AccID3norm[AccID3norm$Vagueness == v & AccID3norm$TimePressure == tp,] #  & AccID3$V3scld > 0.2
    acc <- c()
    Ntrial <- c()
    v3vec <- seq(0,1,.015)
    for (v3 in v3vec)
    {
      mask <- onesect$V3scld > v3 -.15 & onesect$V3scld < v3 + .15
      Ntrial <- rbind(Ntrial, sum(mask)*15)
      acc <- rbind(acc, weighted.mean(onesect[mask,]$acc,onesect[mask,]$Ntrial))
    }
    cut <- Ntrial > 200
    Sldwndwdat <- rbind(Sldwndwdat, data.frame(v3 = v3vec[cut], acc = acc[cut], Ntrial = Ntrial[cut], TimePressure = tp, Vagueness = v))
    
    if (vi == 1 & tpi == 1){plot(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol, xlim = c(0, 1.1), ylim = c(-.04,.04), xlab = 'Sliding window on scaled V3', ylab = '% Correct | (1, 2)')}else{points(v3vec[cut], acc[cut], cex = (Ntrial[cut])/600, col = mycol)}
    lines(v3vec[cut], acc[cut], col = mycol)
    test <- lm(acc[cut] ~ v3vec[cut], weights = Ntrial[cut])
    abline(test, col = mycol)
  }
}
legend('bottom',c('Precise-Low','Vague-Low','Precise-High','Vauge-High'), cex = .8, text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("ChoiceNorm~IDV3scldtomin_SldWndwWght.pdf")),height=4, width=4)
dev.off()
```

# Aggregated accuracy over V3 quantiles, pooled all subjects
```{r}
qv3 <- quantile(grpdcsn$V3, c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1))
qv <- (qv3[1:(length(qv3)-1)] + qv3[2:length(qv3)])/2
grpdcsn$qv3 <- 0
grpdcsn$qv3[grpdcsn$V3 >= qv3[1] & grpdcsn$V3 < qv3[2]] <- .05
grpdcsn$qv3[grpdcsn$V3 >= qv3[2] & grpdcsn$V3 < qv3[3]] <- .15
grpdcsn$qv3[grpdcsn$V3 >= qv3[3] & grpdcsn$V3 < qv3[4]] <- .25
grpdcsn$qv3[grpdcsn$V3 >= qv3[4] & grpdcsn$V3 < qv3[5]] <- .35
grpdcsn$qv3[grpdcsn$V3 >= qv3[5] & grpdcsn$V3 <= qv3[6]] <- .45
grpdcsn$qv3[grpdcsn$V3 >= qv3[6] & grpdcsn$V3 <= qv3[7]] <- .55
grpdcsn$qv3[grpdcsn$V3 >= qv3[7] & grpdcsn$V3 <= qv3[8]] <- .65
grpdcsn$qv3[grpdcsn$V3 >= qv3[8] & grpdcsn$V3 <= qv3[9]] <- .75
grpdcsn$qv3[grpdcsn$V3 >= qv3[9] & grpdcsn$V3 <= qv3[10]] <- .85
grpdcsn$qv3[grpdcsn$V3 >= qv3[10] & grpdcsn$V3 <= qv3[11]] <- .95
table(grpdcsn$qv3)
for (tp in c('Low','High'))
{
  for (v in c('Precise','Vague'))
  {
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    
    subdat <- grpdcsn[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v & grpdcsn$chosenItem != 3 & !is.nan(grpdcsn$chosenItem), ]
    show(length(subdat$subID))
    acc <- aggregate(choice ~ qv3, data = subdat, FUN = mean)
    acc$mqv3 <- quantile(subdat$V3, acc$qv3)
    if (tp == 'Low' & v == 'Precise'){plot(choice ~ mqv3, data = acc, type = 'b', col = mycol, ylim = c(.601,.75), xlab = 'V3', ylab = '% Correct | (1, 2)')}else{lines(choice ~ mqv3, data = acc, type = 'b', col = mycol)}
  }
}
legend('top',c('Precise-Low','Vague-Low','Precise-High','Vauge-High'), cex = .8, text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Choice~V3_Qntls.pdf")),height=4, width=4)
dev.off()
```
# Aggregated accuracy over scaled V3 quantiles, pooled all subjects
```{r}
qv3 <- quantile(grpdcsn$V3scld, c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1))
qv <- (qv3[1:(length(qv3)-1)] + qv3[2:length(qv3)])/2
grpdcsn$qv3 <- 0

grpdcsn$qv3[grpdcsn$V3scld >= qv3[1] & grpdcsn$V3scld < qv3[2]] <- .05
grpdcsn$qv3[grpdcsn$V3scld >= qv3[2] & grpdcsn$V3scld < qv3[3]] <- .15
grpdcsn$qv3[grpdcsn$V3scld >= qv3[3] & grpdcsn$V3scld < qv3[4]] <- .25
grpdcsn$qv3[grpdcsn$V3scld >= qv3[4] & grpdcsn$V3scld < qv3[5]] <- .35
grpdcsn$qv3[grpdcsn$V3scld >= qv3[5] & grpdcsn$V3scld <= qv3[6]] <- .45
grpdcsn$qv3[grpdcsn$V3scld >= qv3[6] & grpdcsn$V3scld <= qv3[7]] <- .55
grpdcsn$qv3[grpdcsn$V3scld >= qv3[7] & grpdcsn$V3scld <= qv3[8]] <- .65
grpdcsn$qv3[grpdcsn$V3scld >= qv3[8] & grpdcsn$V3scld <= qv3[9]] <- .75
grpdcsn$qv3[grpdcsn$V3scld >= qv3[9] & grpdcsn$V3scld <= qv3[10]] <- .85
grpdcsn$qv3[grpdcsn$V3scld >= qv3[10] & grpdcsn$V3scld <= qv3[11]] <- .95
table(grpdcsn$qv3)
for (tp in c('Low','High'))
{
  for (v in c('Precise','Vague'))
  {
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    
    subdat <- grpdcsn[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v  & grpdcsn$chosenItem != 3 & !is.nan(grpdcsn$chosenItem), ]
    show(length(subdat$subID))
    acc <- aggregate(choice ~ qv3, data = subdat, FUN = mean)
    N <- aggregate(choice ~ qv3, data = subdat, FUN = length)
    acc$mqv3 <- quantile(subdat$V3scld, acc$qv3)
    
    if (tp == 'Low' & v == 'Precise'){plot(choice ~ mqv3, data = acc, type = 'b', col = mycol, ylim = c(.59,.75), xlab = 'Scaled V3', ylab = '% Correct | (1, 2)')}else{lines(choice ~ mqv3, data = acc, type = 'b', col = mycol)}
  }
}
legend('top',c('Precise-Low','Vague-Low','Precise-High','Vauge-High'), cex = .8, text.col = c('red','blue','pink','lightblue'), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Choice~V3scldtomin_Qntls.pdf")),height=4, width=4)
dev.off()
```
# Aggregated accuracy over normV3 quantiles, pooled all subjects
```{r}
qv3 <- quantile(grpdcsn$normv3, c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1))
qv <- (qv3[1:(length(qv3)-1)] + qv3[2:length(qv3)])/2
grpdcsn$qv3 <- 0

grpdcsn$qv3[grpdcsn$normv3 >= qv3[1] & grpdcsn$normv3 < qv3[2]] <- .05
grpdcsn$qv3[grpdcsn$normv3 >= qv3[2] & grpdcsn$normv3 < qv3[3]] <- .15
grpdcsn$qv3[grpdcsn$normv3 >= qv3[3] & grpdcsn$normv3 < qv3[4]] <- .25
grpdcsn$qv3[grpdcsn$normv3 >= qv3[4] & grpdcsn$normv3 < qv3[5]] <- .35
grpdcsn$qv3[grpdcsn$normv3 >= qv3[5] & grpdcsn$normv3 <= qv3[6]] <- .45
grpdcsn$qv3[grpdcsn$normv3 >= qv3[6] & grpdcsn$normv3 <= qv3[7]] <- .55
grpdcsn$qv3[grpdcsn$normv3 >= qv3[7] & grpdcsn$normv3 <= qv3[8]] <- .65
grpdcsn$qv3[grpdcsn$normv3 >= qv3[8] & grpdcsn$normv3 <= qv3[9]] <- .75
grpdcsn$qv3[grpdcsn$normv3 >= qv3[9] & grpdcsn$normv3 <= qv3[10]] <- .85
grpdcsn$qv3[grpdcsn$normv3 >= qv3[10] & grpdcsn$normv3 <= qv3[11]] <- .95
table(grpdcsn$qv3)
for (tp in c('Low','High'))
{
  for (v in c('Precise','Vague'))
  {
    if (v == 'Vague' & tp == 'Low'){mycol <- 'blue'}
    if (v == 'Precise' & tp == 'High'){mycol <- 'pink'}
    if (v == 'Precise' & tp == 'Low'){mycol <- 'red'}
    if (v == 'Vague' & tp == 'High'){mycol <- 'lightblue'}
    
    subdat <- grpdcsn[grpdcsn$TimePressure == tp & grpdcsn$Vagueness == v  & grpdcsn$chosenItem != 3 & !is.nan(grpdcsn$chosenItem), ]
    show(length(subdat$subID))
    acc <- aggregate(choice ~ qv3, data = subdat, FUN = mean)
    acc$mqv3 <- quantile(subdat$V3scld, acc$qv3)
    if (tp == 'Low' & v == 'Precise'){plot(choice ~ mqv3, data = acc, type = 'b', col = mycol, xlim = c(0, 1.1), ylim = c(.6,.75), xlab = 'Norm V3', ylab = '% Correct | (1, 2)')}else{lines(choice ~ mqv3, data = acc, type = 'b', col = mycol)}
  }
}
dev.copy(pdf,file.path(out_dir,sprintf("Choice~normV3_Qntls.pdf")),height=4, width=4)
dev.off()
```

# diagram
```{r}
subjlist <- unique(grpbid$subID)

indvdat <- grpbid[grpbid$subID == subjlist[2],]
mbid <- aggregate(bid ~ item + touched, data = indvdat, FUN = mean)
mask <- mbid$touched == 1
plot(mbid$bid[mask], mbid$bid[mask], pch = 20, cex = 1, col = 2, xlab = "", ylab = "", xaxt = "n", yaxt = "n")
axis(1, at = seq(0,80,20), tck = -0.03, padj = -1.118, cex.axis = 1)
axis(2, tck = -0.03, at = seq(0,80,20), padj = 1.118, cex.axis = 1)
title(xlab = 'Bid mean ($)', ylab = 'Bid mean ($)', mgp = c(1.38,0,0), font.lab = 1, cex.lab = 1)

undat <- mbid[mbid$touched == 0,]
mask <- rank(undat$bid)<13
points(undat$bid[mask], undat$bid[mask], pch = 20, cex = 1, col = 3)
legend('topleft', c('Interactive','Non-Interactive'), pch = 20, col = c(2,3), text.col = c(2,3), bty = 'n')
dev.copy(pdf,file.path(out_dir,sprintf("Diagram.pdf")),height=3.4, width=3.4)
dev.off()
```

## Model fitting results
```{r}
out_dir <- '/Users/bs3667/Noise/modelfit/Results/FastBADS_Mtlb/plot'
fastbads <- read.table('/Users/bs3667/Noise/modelfit/Results/FastBADS_Mtlb/Rslts_FastBADS_Best.txt', header = TRUE, sep = '\t')
fastbads <- fastbads[fastbads$subID < 48,]
fastbads$subID <- as.factor(fastbads$subID)
fastbads$name <- factor(fastbads$name, levels = c('McFadden','Model2','DN','dDNa','dDNb','dDNc','dDNd'))
fastbads$modeli <- as.factor(fastbads$modeli)
str(fastbads)
summary(test <- aov(nll ~ name + Error(subID), data = fastbads))
names <- unique(fastbads$name)
subjlist <- unique(fastbads$subID)

par(mfrow=c(3,2))
for (mdli in 1)
{
  for (mdlj in 2:7)
  {
    bars <- fastbads$nll[fastbads$modeli == mdlj] - fastbads$nll[fastbads$modeli == mdli]
    barplot(bars, ylab = 'nLL', xlab = 'Subjects', names = subjlist, main = sprintf('%s - %s', names[mdlj], names[mdli]))
    legend('bottomleft',sprintf('delta nLL = %1.3f', sum(bars)), bty = 'n')
    # plot(fastbads$nll[fastbads$modeli==mdli], fastbads$nll[fastbads$modeli==mdlj], type = 'p', pch = 20, xlab = names[mdli], ylab = names[mdlj], xlim = range(c(fastbads$nll[fastbads$modeli==mdli], fastbads$nll[fastbads$modeli==mdlj])), ylim = range(c(fastbads$nll[fastbads$modeli==mdli], fastbads$nll[fastbads$modeli==mdlj])))
    # abline(a = 0, b = 1, lty = 1)
  }
}

par(mfrow=c(3,2))
for (mdli in 2)
{
  for (mdlj in 3:7)
  {
    bars <- fastbads$nll[fastbads$modeli == mdlj] - fastbads$nll[fastbads$modeli == mdli]
    barplot(bars, ylab = 'nLL', xlab = 'Subjects', names = subjlist, main = sprintf('%s - %s', names[mdlj], names[mdli]))
    legend('bottomleft',sprintf('delta nLL = %1.3f', sum(bars)), bty = 'n')
  }
}

par(mfrow=c(2,2))
for (mdli in 3)
{
  for (mdlj in 4:7)
  {
    bars <- fastbads$nll[fastbads$modeli == mdlj] - fastbads$nll[fastbads$modeli == mdli]
    barplot(bars, ylab = 'nLL', xlab = 'Subjects', names = subjlist, main = sprintf('%s - %s', names[mdlj], names[mdli]))
    legend('bottomleft',sprintf('delta nLL = %1.3f', sum(bars)), bty = 'n')
  }
}

par(mfrow=c(1,2))
for (mdli in 1:2)
{
  bars <- fastbads$eta[fastbads$modeli == mdli]
  plot(density(bars), xlab = 'eta', main = names[mdli], bty = 'n')
  legend('topleft',sprintf('mean eta = %1.1f', mean(bars)), bty = 'n')
}
dev.copy(pdf,file.path(out_dir,sprintf("eta.pdf")),height=3, width=6)
dev.off()

par(mfrow=c(2,3))
for (mdli in 3:7)
{
  bars <- fastbads$Mp[fastbads$modeli == mdli]
  plot(density(bars), xlab = 'Mp', main = names[mdli], bty = 'n')
  legend('topleft',sprintf('mean Mp = %1.1f', mean(bars)), bty = 'n')
}
dev.copy(pdf,file.path(out_dir,sprintf("Mp.pdf")),height=6, width=6)
dev.off()

par(mfrow=c(2,3))
for (mdli in 3:7)
{
  bars <- fastbads$wp[fastbads$modeli == mdli]
  plot(density(bars), xlab = 'wp', main = names[mdli], bty = 'n')
  legend('topleft',sprintf('mean wp = %.3f', mean(bars)), bty = 'n')
}
dev.copy(pdf,file.path(out_dir,sprintf("wp.pdf")),height=6, width=6)
dev.off()

par(mfrow=c(2,2))
for (mdli in 4:7){
plot(fastbads$wp[fastbads$modeli == 3], fastbads$wp[fastbads$modeli == mdli], xlab = names[3], ylab = names[mdli], main = 'wp') 
abline(v = 0, lty = 2)
abline(h = 0, lty = 2)
abline(a = 0, b = 1, lty = 2)}
wp <- aggregate(wp ~ subID, data = fastbads[fastbads$modeli == 3,], FUN = mean)
sort(wp$wp)
```
suspicion of choosing zero V3
```{r}
redtrnsp <- rgb(255,0,0,50, maxColorValue = 255)
bluetrnsp <- rgb(0,0,255,50, maxColorValue = 255)
subjlist <- unique(grpdcsn$subID)
plot(chosenValue ~ subID, data = grpdcsn, type = 'p', pch = 20, las = 2, col = redtrnsp)
points(chosenValue ~ subID, data = grpdcsn[grpdcsn$chosenItem == 3,], pch = 20, col = redtrnsp)
       
table(grpdcsn$subID, grpdcsn$chosenID)

table(indvdcsn$V1, indvdcsn$V2)
slctdat <- indvdcsn[indvdcsn$chosenItem == 2,]
table(slctdat$V1, slctdat$V2)
slctdat <- indvdcsn[indvdcsn$chosenItem == 1,]
table(slctdat$V1, slctdat$V2)

grid <- aggregate(trial ~ V1 + V2 + chosenItem, data = indvdcsn, FUN = length)

mydat <- indvdcsn
mydat$V1 <- mydat$V1 + rnorm(length(mydat$V1), 0, mydat$V1/10)
mydat$V2 <- mydat$V2 + rnorm(length(mydat$V2), 0, mydat$V2/10)
plot(V2 ~ V1, col = bluetrnsp, pch = 20, data = mydat[mydat$chosenItem == 2,])
points(V2 ~ V1, col = redtrnsp, pch = 20, data = mydat[mydat$chosenItem == 1,])
points(V2 ~ V1, col = "red", pch = 20, data = mydat[mydat$chosenItem == 3,])
```

